Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-06-28 paper/paper.tex
WIP - getting my expression profiles all in the right sense

\textbf{Another approach:} We present a model of gradient-following based on graded
interactions between the growth cones of retinal ganglion cell axons and the
tectal surface. We show that a combination of exponentially graded expression
in the retina and logarithmically graded expression on the tectum permits a
purely local model to reproduce the majority of reported phenomena associated
with retinotectal organisation.

@@

>>>>

\textbf{Another approach:} We present a model of gradient-following based on graded
interactions between the growth cones of retinal ganglion cell axons and the
tectal surface. We show that a combination of exponentially graded expression
in the retina~\cite{reber_relative_2004} and exponentially (for repulsively
interacting receptor ligand pairs) \emph{or} logarithmically (for attractively
interacting receptor/ligands) graded expression on the tectum permits a purely
local model to reproduce the majority of reported phenomena associated with
retinotectal organisation.

@@

Interactions in the model are by receptor-ligand interactions only. Forward
interactions are those in which the ligand activates the receptor, delivering
a signal into the receptor-expressing cell. Reverse signals occur when a
membrane-bound ligand is activated~\cite{wu_role_2019}.
